---
title: "Untitled"
author: "Margaret Janiczek"
date: "2025-05-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(igraph)
library(matrixcalc)
library(ggcorrplot)
```


Specify number of vertices and subnetworks

Vertices: 100
Subnetworks:4

Using `sample.pa` function from `igraph` package, which uses a simple algorithm ("Preferential attachment") from Barabasi to generate a graph. It is a discrete time step model and in each time step a vertex is added. 

* starts with a single vertex and no edges
* adds a vertex in each time step and initiate some edges to old vertices
* probability that old vertex is chosen given by: $P[i] \sim k_i^{\alpha} + a$
* in each time step specify number of edges initiated or probability of a number of edges added.
* specify if directed or undirected graph.

Network generation parameters:

n = number of vertices
m = number of edges to add in each step


```{r}

set.seed(1219)

#number of vertices
p <- 100
#number of subnetworks
L <- 4
p_sub <- p / L

m <- 2
power <- 1

vsize <- 2
par(mar = c(1, 1, 1, 1) + 0.5)


# run algorithm on each subnetwork and join to make one network
Omega_sub <- vector(mode = "list", length = L)
for (l in 1:L) {
  # barabasi was deprecated in igraph 2.0.0. says to use "sample_pa()" instead
    G <- as.matrix(as_adjacency_matrix(sample_pa(p_sub, 
                                                     power = power, m = m, 
                                                     directed = FALSE)))
    size <- sum(G) / 2
    
    a <- 0.6
    b <-  0.9
    samp_right <- runif(ceiling(size / 2), min = a, max = b)
    samp_left <- runif(ceiling(size / 2), min = -b, max = -a)
    samp <- sample(c(samp_left, samp_right), size)
    ind <- 1
    for (i in 2:p_sub) {
        for (j in 1:(i - 1)) {
            if (G[i, j] != 0) {
                G[i, j] <- G[j, i] <- samp[ind]
                ind <- ind + 1
            }
        }
    }
    
    Omega_sub[[l]] <- G
}

Omega1 <- matrix(0, nrow = p, ncol = p)
for (l in 1:L) {
    Omega1[((l - 1) * p_sub + 1):(l * p_sub), 
           ((l - 1) * p_sub + 1):(l * p_sub)] <- Omega_sub[[l]]
}
ggcorrplot(Omega1)
```


```{r}
# get non-zero values and make adjacency matrix
G1 <- Omega1 != 0
G1_graph <- graph_from_adjacency_matrix(G1, mode = "undirected")
gsize(G1_graph)
layout <- layout_nicely(G1_graph)
plot(G1_graph, vertex.frame.color = "white", 
     layout = layout,
     vertex.label = NA, vertex.color = "dodgerblue4", vertex.size = vsize,
     edge.width = 3)
```

Check if matrix is positive definite, and if not, add a small value
```{r}
is.positive.definite(Omega1)
diag(Omega1) <- rowSums(abs(Omega1)) + 0.1
is.positive.definite(Omega1)
ggcorrplot(Omega1)
```

Now use `solve()` function to get inverse i.e. Precision matrix.

```{r}
Sigma1 <- solve(Omega1)
ggcorrplot(Sigma1)
```

Now generate second graph. Use`rewire` function in `igraph` package and `keeping_degseq` method which randomly rewires 

```{r}

p <-  100
#L <-  4
#p_sub <-  p / L

G2_graph <- rewire(G1_graph, keeping_degseq(niter = 30))
G_diff_graph <- igraph::union(igraph::difference(G1_graph, G2_graph), 
                        igraph::difference(G2_graph, G1_graph))
gsize(G_diff_graph)
G2 <- as.matrix(as_adjacency_matrix(G2_graph))
G_diff <- as.matrix(as_adjacency_matrix(G_diff_graph))
{
    common <- intersection(G1_graph, G2_graph)
    E(common)$color <- 1
    
    diff21 <- add_edges(common, 
                        as.vector(t(as_edgelist(difference(G2_graph, G1_graph)))),
                        color = "2")
    diff12 <- add_edges(common, 
                        as.vector(t(as_edgelist(difference(G1_graph, G2_graph)))),
                        color = "2")
    vsize <- 2
    
    plot(diff12, vertex.frame.color = "white", 
         layout = layout, 
         vertex.label = NA, vertex.color = "dodgerblue4", vertex.size = vsize,
         edge.width = 3)
    
    plot(diff21, vertex.frame.color = "white", 
         layout = layout, 
         vertex.label = NA, vertex.color = "dodgerblue4", vertex.size = vsize,
         edge.width = 3)
    
    E(G_diff_graph)$color <- 2
    plot(G_diff_graph, vertex.frame.color = "white", 
         layout = layout, 
         vertex.label = NA, vertex.color = "dodgerblue4", vertex.size = vsize,
         edge.width = 3)
    
}

ggcorrplot(Omega1)
diag(G2) <- 1
Omega2 <- Omega1 * G2
ggcorrplot(Omega2)
diag(G2) <- 0
ggcorrplot(G2)

size <- gsize(G_diff_graph)

a <- 0.6
b <- 0.9
samp_right <- runif(ceiling(size / 2), min = a, max = b)
samp_left <- runif(ceiling(size / 2), min = -b, max = -a)
samp <- sample(c(samp_left, samp_right), size)
ind <-  1
for (i in 2:p) {
    for (j in 1:(i - 1)) {
        if (G2[i, j] != 0 & G1[i, j] == 0) {
            Omega2[i, j] <- Omega2[j, i] <- samp[ind]
            ind <- ind + 1
        }
    }
}

is.positive.definite(Omega1)
is.positive.definite(Omega2)
#diag(Omega2) <- diag(Omega2) + 0.1
is.positive.definite(Omega2)
ggcorrplot(Omega1)
ggcorrplot(Omega2)

ggcorrplot(Sigma1)
Sigma2 <-  solve(Omega2)
ggcorrplot(Sigma2)
```

