---
title: "Example simulation setup"
output: pdf_document
date: "2025-05-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(jewel)
library(tidyverse)
library(JGL)
library(pROC)
library(pheatmap)
library(MASS)

library(spikeyglass)

source("00_helper_functions.R")
source("01_generate_gold_standard_networks.R")

# read in reference weights
realDataHist = read.csv("mxDist.csv")
lower <- quantile(weights, .25)
upper <- quantile(weights, .75)

upper <- 0.035
new_realdat <- realDataHist %>%
  filter(abs(mids) > upper) 

min_weight <- min(new_realdat$density[new_realdat$density > 0])

new_realdat <- new_realdat %>%
  mutate(density = ifelse(density ==0, min_weight, density))
```

Generate gold standard networks


First generate graph for network 1. We are generating under 2 different topologies: random or scale free. 

```{r}
set.seed(1219)

# low density
dens1 = 0.06

# high density
dens2 = 0.2

# percent of edges to rewire
perc <- 0.1
  
K <- 2 # number of groups
p <- 50# number of vertices
n <- 1000 # number of samples per group

# number of subnetworks
L <- 4
p_sub <- p/L  # features per subnetwork


# percent of edges to rewire
perc <- 0.1

g1_random_low = sample_gnp(p, dens1)
g1_random_high = sample_gnp(p, dens2)

g1_islands = sample_islands(4, round(p/4, 0), 5/10, 1)

g1_sf_low = sample_pa(n=p, power=1, m=2, directed=F)
g1_sf_high = sample_pa(n=p, power=1, m=5, directed=F)


plot(g1_random_low, layout = layout_in_circle)
plot(g1_random_high, layout = layout_in_circle)
plot(g1_sf_low, layout = layout_in_circle)
plot(g1_sf_high, layout = layout_in_circle)
plot(g1_islands, layout = layout_in_circle)


g_list <- list(random_low = g1_random_low,
               random_high = g1_random_high,
               sf_low = g1_sf_low,
               sf_high = g1_sf_high)

```

```{r}
gold_list_uniform <- map(g_list, ~gen_gold(.x, .1, new_realdat, wt_method = "uniform"))
gold_list_empirical <- map(g_list, ~gen_gold(.x, .1, new_realdat, wt_method = "empirical"))

lam1= 1
lam.eff <- lam1 + c(1:5) * 5
v0s <- lam1/lam.eff



# res_reps_p50_n1000_1 <- get_results(p, n, gold_list_uniform = gold_list_uniform, gold_list_empirical = gold_list_empirical, v0s, 3)
# 
# 
#   library(pbmcapply)
#      library(parallel)
#      ncores <- detectCores()
# 
# rest_test <- list()
# result_test <- pbmclapply(1:2, get_results(p, n, gold_list_uniform = gold_list_uniform, gold_list_empirical = gold_list_empirical, v0s, 3), mc.cores = ncores-1)
# 
# 
# rest_test <- list() #for lambda2
# 
# MC_results <- pbmclapply(1:2, function(i){get_results(p, n, gold_list_uniform = gold_list_uniform, gold_list_empirical = gold_list_empirical, v0s, 3)} # Use <<- to assign to the outer scope
# , mc.cores = detectCores() - 1)
# 
# rest_test <- c(1:10)




## 100, 1000
set.seed(12)
p <- 100# number of vertices
n <- 1000 # number of samples per group

# percent of edges to rewire
perc <- 0.1

g1_random_low = sample_gnp(p, dens1)
g1_random_high = sample_gnp(p, dens2)
g1_sf_low = sample_pa(n=p, power=1, m=2, directed=F)
g1_sf_high = sample_pa(n=p, power=1, m=5, directed=F)


g_list <- list(random_low = g1_random_low,
               random_high = g1_random_high,
               sf_low = g1_sf_low,
               sf_high = g1_sf_high)

gold_list_uniform_100 <- map(g_list, ~gen_gold(.x, .1, new_realdat, wt_method = "uniform"))
gold_list_empirical_100 <- map(g_list, ~gen_gold(.x, .1, new_realdat, wt_method = "empirical"))


res_reps_p100_n1000_1 <- get_results(p, n, gold_list_uniform = gold_list_uniform_100, gold_list_empirical = gold_list_empirical_100, v0s, 3)

res_reps_p100_n1000_2 <- get_results(p, n, gold_list_uniform = gold_list_uniform_100, gold_list_empirical = gold_list_empirical_100, v0s, 3)

res_reps_p100_n1000_3 <- get_results(p, n, gold_list_uniform = gold_list_uniform_100, gold_list_empirical = gold_list_empirical_100, v0s, 3)

res_reps_p100_n1000_4 <- get_results(p, n, gold_list_uniform = gold_list_uniform_100, gold_list_empirical = gold_list_empirical_100, v0s, 3)

res_reps_p100_n1000_5 <- get_results(p, n, gold_list_uniform = gold_list_uniform_100, gold_list_empirical = gold_list_empirical_100, v0s, 3)

res_reps_p100_n1000_6 <- get_results(p, n, gold_list_uniform = gold_list_uniform_100, gold_list_empirical = gold_list_empirical_100, v0s, 3)

res_reps_p100_n1000_7 <- get_results(p, n, gold_list_uniform = gold_list_uniform_100, gold_list_empirical = gold_list_empirical_100, v0s, 3)

res_reps_p100_n1000_8 <- get_results(p, n, gold_list_uniform = gold_list_uniform_100, gold_list_empirical = gold_list_empirical_100, v0s, 3)

res_reps_p100_n1000_9 <- get_results(p, n, gold_list_uniform = gold_list_uniform_100, gold_list_empirical = gold_list_empirical_100, v0s, 3)

res_reps_p100_n1000_10 <- get_results(p, n, gold_list_uniform = gold_list_uniform_100, gold_list_empirical = gold_list_empirical_100, v0s, 3)


res_master_list_100_2 <- bind_rows(res_reps_p100_n1000_1,
                             res_reps_p100_n1000_2,
                             res_reps_p100_n1000_3,
                             res_reps_p100_n1000_4,
                             res_reps_p100_n1000_5,
                             res_reps_p100_n1000_6,
                             res_reps_p100_n1000_7,
                             res_reps_p100_n1000_8,
                             res_reps_p100_n1000_9,
                             res_reps_p100_n1000_10)


save(res_master_list_100_2, file = "res_master_list_p100_2_n1000.Rdata")



res_master_list_100_total <- res_master_list_100 %>%
  #bind_rows(res_master_list_100_2) %>%
  mutate(
    avg_tpr = (tpr1 + tpr2)/2, 
    avg_fpr = (fpr1 + fpr2)/2,
    avg_auc = (auc1 + auc2)/2
  )

list_100 <- res_master_list_100_total %>%
  dplyr::select(data, setting, method, n, p, avg_tpr, avg_fpr, avg_auc) %>%
  #separate_wider_delim(data, delim = "_", names = c("weights", "density")) %>%
  pivot_longer(cols = starts_with("avg")) %>%
  mutate(setting = fct_relevel(as.factor(setting), "uniform"),
         name = fct_relevel(as.factor(name), "avg_tpr", "avg_fpr")) %>%
  mutate(method = fct_recode(method, ssjgl = "sjgl"),
         setting = fct_recode(setting, empirical = "emp"))



ggplot(list_100) +
       # %>%filter(setting == "emp")) +
  geom_boxplot(aes(y = value, x = name, fill = method) ) +
  facet_wrap(~setting + data, nrow = 2) + 
  theme_bw()

# 50 

res_master_list_50_total <- res_master_list %>%
  #bind_rows(res_master_list_50_2) %>%
  mutate(
    avg_tpr = (tpr1 + tpr2)/2, 
    avg_fpr = (fpr1 + fpr2)/2,
    avg_auc = (auc1 + auc2)/2
  )

list_50 <- res_master_list_50_total %>%
  dplyr::select(data, setting, method, n, p, avg_tpr, avg_fpr, avg_auc) %>%
  #separate_wider_delim(data, delim = "_", names = c("weights", "density")) %>%
  pivot_longer(cols = starts_with("avg")) %>%
  mutate(setting = fct_relevel(as.factor(setting), "uniform"),
         name = fct_relevel(as.factor(name), "avg_tpr", "avg_fpr")) %>%
  mutate(method = fct_recode(method, ssjgl = "sjgl"))


ggplot(list_50) +
       # %>%filter(setting == "emp")) +
  geom_boxplot(aes(y = value, x = name, fill = method) ) +
  facet_wrap(~setting + data, nrow = 2) + 
  theme_bw()
#err_res <- nab_error_mets(res_reps, 3, gold_list_uniform = gold_list_uniform, gold_list_empirical = gold_list_empirical)
```


```{r}
## 100, 1000

p <- 50# number of vertices
n <- 10000 # number of samples per group

# percent of edges to rewire
perc <- 0.1

g1_random_low = sample_gnp(p, dens1)
g1_random_high = sample_gnp(p, dens2)
g1_sf_low = sample_pa(n=p, power=1, m=2, directed=F)
g1_sf_high = sample_pa(n=p, power=1, m=5, directed=F)


g_list <- list(random_low = g1_random_low,
               random_high = g1_random_high,
               sf_low = g1_sf_low,
               sf_high = g1_sf_high)

gold_list_uniform_1000 <- map(g_list, ~gen_gold(.x, .1, new_realdat, wt_method = "uniform"))
gold_list_empirical_1000 <- map(g_list, ~gen_gold(.x, .1, new_realdat, wt_method = "empirical"))


res_reps_p50_n10000_1 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p50_n10000_2 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p50_n10000_3 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p50_n10000_4 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p50_n10000_5 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p50_n10000_6 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p50_n10000_7 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p50_n10000_8 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p50_n10000_9 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p50_n10000_10 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)


res_master_list_p50n10000 <- bind_rows(res_reps_p50_n10000_1,
                             res_reps_p50_n10000_2,
                             res_reps_p50_n10000_3,
                             res_reps_p50_n10000_4,
                             res_reps_p50_n10000_5,
                             res_reps_p50_n10000_6,
                             res_reps_p50_n10000_7,
                             res_reps_p50_n10000_8,
                             res_reps_p50_n10000_9,
                             res_reps_p50_n10000_10)


save(res_master_list_p50n10000, file = "res_master_list_p50_n10000.Rdata")



res_master_list_50_10000 <- res_master_list_p50n10000 %>%
  mutate(
    avg_tpr = (tpr1 + tpr2)/2, 
    avg_fpr = (fpr1 + fpr2)/2,
    avg_auc = (auc1 + auc2)/2
  )

list_50_1000 <- res_master_list_50_10000 %>%
  dplyr::select(data, setting, method, n, p, avg_tpr, avg_fpr, avg_auc) %>%
  #separate_wider_delim(data, delim = "_", names = c("weights", "density")) %>%
  pivot_longer(cols = starts_with("avg"))

ggplot(list_50_1000) +
       # %>%filter(setting == "emp")) +
  geom_boxplot(aes(y = value, x = name, fill = method) ) +
  facet_wrap(~setting + data, nrow = 2) + 
  theme_bw()
```

```{r}
p <- 200# number of vertices
n <- 10000 # number of samples per group

# percent of edges to rewire
perc <- 0.1

g1_random_low = sample_gnp(p, dens1)
g1_random_high = sample_gnp(p, dens2)
g1_sf_low = sample_pa(n=p, power=1, m=2, directed=F)
g1_sf_high = sample_pa(n=p, power=1, m=5, directed=F)


g_list <- list(random_low = g1_random_low,
               random_high = g1_random_high,
               sf_low = g1_sf_low,
               sf_high = g1_sf_high)

gold_list_uniform_1000 <- map(g_list, ~gen_gold(.x, .1, new_realdat, wt_method = "uniform"))
gold_list_empirical_1000 <- map(g_list, ~gen_gold(.x, .1, new_realdat, wt_method = "empirical"))


res_reps_p200_n10000_1 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p200_n10000_2 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p200_n10000_3 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p100_n10000_4 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p100_n10000_5 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p100_n10000_6 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p100_n10000_7 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p100_n10000_8 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p100_n10000_9 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)

res_reps_p100_n10000_10 <- get_results(p, n, gold_list_uniform = gold_list_uniform_1000, gold_list_empirical = gold_list_empirical_1000, v0s, 3)


res_master_list_p50n10000 <- bind_rows(res_reps_p100_n10000_1,
                             res_reps_p100_n10000_2,
                             res_reps_p100_n10000_3,
                             res_reps_p100_n10000_4,
                             res_reps_p100_n10000_5,
                             res_reps_p100_n10000_6,
                             res_reps_p100_n10000_7,
                             res_reps_p100_n10000_8,
                             res_reps_p100_n10000_9,
                             res_reps_p100_n10000_10)


save(res_master_list_p50n10000, file = "res_master_list_p50_n10000.Rdata")



res_master_list_100 <- res_master_list_100 %>%
  mutate(
    avg_tpr = (tpr1 + tpr2)/2, 
    avg_fpr = (fpr1 + fpr2)/2,
    avg_auc = (auc1 + auc2)/2
  )

list_100 <- res_master_list_100 %>%
  dplyr::select(data, setting, method, n, p, avg_tpr, avg_fpr, avg_auc) %>%
  #separate_wider_delim(data, delim = "_", names = c("weights", "density")) %>%
  pivot_longer(cols = starts_with("avg"))

ggplot(list_100 %>%filter(setting == "emp")) +
  geom_boxplot(aes(y = value, x = data, fill = method) ) +
  facet_wrap(~name) + 
  theme_bw()
```





Now rewire the G1 graph to get G2, then set edge weights in two ways: one using empirical distribution (Shutta) and another using uniform distribution (Plaksienko). 

```{r}

gold_list_uniform <- map(g_list, ~gen_gold(.x, .1, new_realdat, wt_method = "uniform"))
gold_list_empirical <- map(g_list, ~gen_gold(.x, .1, new_realdat, wt_method = "empirical"))

#generate data

dat_list_uniform <- map(gold_list_uniform, ~gen_dat(.x, n))
dat_list_empirical <- map(gold_list_empirical, ~gen_dat(.x, n))

# just run this tuning on one dataset
lam_list_unif <- map(dat_list_uniform, ~tune_jgl(.x))
lam_list_emp <- map(dat_list_empirical, ~tune_jgl(.x))

jgl_res_unif <- map2(dat_list_uniform, lam_list_unif, ~JGL(Y=.x,
               penalty="fused",
               lambda1= .y$lam_1,
               lambda2= .y$lam_2,
               return.whole.theta=TRUE))

jgl_res_emp <- map2(dat_list_empirical, lam_list_emp, ~JGL(Y=.x,
               penalty="fused",
               lambda1= .y$lam_1,
               lambda2= .y$lam_2,
               return.whole.theta=TRUE))


lam1= 1
lam.eff <- lam1 + c(1:10) * 5
v0s <- lam1/lam.eff

tic()
ssjgl_res_emp <- map(dat_list_empirical, ~ ssjgl(Y=.x,penalty="fused",lambda0=1, lambda1=1,
                     lambda2=1, v1 = 1, v0s = v0s, a=1, b=1, doubly=TRUE, normalize=FALSE))
toc()

#save(ssjgl_res_emp, file = "ssjgl_res_emp_500_1000.Rdata")
# tic()
# ssjgl_res_emp_otherv0 <- map(dat_list_empirical, ~ ssjgl(Y=.x,penalty="fused",lambda0=1, lambda1=1,
#                      lambda2=1, v1 = 1, v0s = seq(1e-04, 0.01, len = 10), a=1, b=1, doubly=TRUE, normalize=FALSE))
# toc()

tic()
ssjgl_res_unif <- map(dat_list_uniform, ~ ssjgl(Y=.x,penalty="fused",lambda0=1, lambda1=1,
                     lambda2=1, v1 = 1, v0s = v0s, a=1, b=1, doubly=TRUE, normalize=FALSE))
toc()

# tic()
# ssjgl_res_unif_otherv0 <- map(dat_list_uniform, ~ ssjgl(Y=.x,penalty="fused",lambda0=1, lambda1=1,
#                      lambda2=1, v1 = 1, v0s = seq(1e-04, 0.01, len = 10), a=1, b=1, doubly=TRUE, normalize=FALSE))
# toc()




jgl_res_err_unif <- map2(jgl_res_unif,gold_list_uniform, ~calc_metrics(.x$theta, .y, 0.01, "uniform", 0.1)) %>%
  bind_rows(.id = "data") %>%
  mutate(method = "jgl")

ssjgl_res_err_unif <- map2(ssjgl_res_unif, gold_list_uniform, ~calc_metrics(.x$thetalist[[3]], .y, .01, "uniform", 0.1))%>%
  bind_rows(.id = "data") %>%
  mutate(method = "sjgl")

jgl_res_err_emp <- map2(jgl_res_emp,gold_list_empirical, ~calc_metrics(.x$theta, .y, 0.01, "empirical", 0.1))%>%
  bind_rows(.id = "data") %>%
  mutate(method = "jgl")

ssjgl_res_err_emp <- map2(ssjgl_res_emp, gold_list_empirical, ~calc_metrics(.x$thetalist[[3]], .y, .01, "empirical", 0.1))%>%
  bind_rows(.id = "data") %>%
  mutate(method = "sjgl")

# ssjgl_res_err_emp_otherv <- map2(ssjgl_res_emp_otherv0, gold_list_empirical, ~calc_metrics(.x$thetalist[[10]], .y, .01, "empirical", 0.03))%>%
#   bind_rows(.id = "data") %>%
#   mutate(method = "sjgl")


res_master_50_1000_10 <- bind_rows(jgl_res_err_unif, ssjgl_res_err_unif, 
                                 jgl_res_err_emp, ssjgl_res_err_emp) %>%
  mutate(p = p,
         n = n)

save(res_master_50_1000_10, file = "res_master_50_1000_10.Rdata")
#save(res_master_100_10000, file = "res_master_100_10000.Rdata")



```


```{r}
res_master_list <- bind_rows(res_master_50_1000,
                             res_master_50_1000_2,
                             res_master_50_1000_3,
                             res_master_50_1000_4,
                             res_master_50_1000_5,
                             res_master_50_1000_6,
                             res_master_50_1000_7,
                             res_master_50_1000_8,
                             res_master_50_1000_9,
                             res_master_50_1000_10)


res_master_list_50 <- res_master_list %>%
  mutate(
    avg_tpr = (tpr1 + tpr2)/2, 
    avg_fpr = (fpr1 + fpr2)/2,
    avg_auc = (auc1 + auc2)/2
  )


list_50 <- res_master_list_50 %>%
  dplyr::select(data, setting, method, n, p, avg_tpr, avg_fpr, avg_auc) %>%
  #separate_wider_delim(data, delim = "_", names = c("weights", "density")) %>%
  pivot_longer(cols = starts_with("avg"))

ggplot(list_50# %>%filter(setting == "empirical")
       ) +
  geom_boxplot(aes(y = value, x = data, fill = method) ) +
  facet_wrap(~setting + name) + 
  theme_bw()

ggplot(list_100# %>%filter(setting == "empirical")
       ) +
  geom_boxplot(aes(y = value, x = data, fill = method) ) +
  facet_wrap(~setting + name) + 
  theme_bw()

ggplot(res_master_list) +
  geom_boxplot(aes(y = auc1, x = data, fill = method) ) +
  facet_wrap(~setting)
```



```{r}

# now run on different sets 

p <- 50# number of vertices
n <- 10000 # number of samples per group

g1_random_low = sample_gnp(p, dens1)
g1_random_high = sample_gnp(p, dens2)
g1_sf_low = sample_pa(n=p, power=1, m=2, directed=F)
g1_sf_high = sample_pa(n=p, power=1, m=5, directed=F)




g_list <- list(random_low = g1_random_low,
               random_high = g1_random_high,
               sf_low = g1_sf_low,
               sf_high = g1_sf_high)

gold_list_uniform <- map(g_list, ~gen_gold(.x, .1, new_realdat, wt_method = "uniform"))
gold_list_empirical <- map(g_list, ~gen_gold(.x, .1, new_realdat, wt_method = "empirical"))

#generate data

dat_list_uniform <- map(gold_list_uniform, ~gen_dat(.x, n))
dat_list_empirical <- map(gold_list_empirical, ~gen_dat(.x, n))

# just run this tuning on one dataset
lam_list_emp <- map(dat_list_empirical, ~tune_jgl(.x))

jgl_res_unif_100 <- map2(dat_list_uniform, lam_list_unif, ~JGL(Y=.x,
               penalty="fused",
               lambda1= .y$lam_1,
               lambda2= .y$lam_2,
               return.whole.theta=TRUE))

jgl_res_emp_100 <- map2(dat_list_empirical, lam_list_emp, ~JGL(Y=.x,
               penalty="fused",
               lambda1= .y$lam_1,
               lambda2= .y$lam_2,
               return.whole.theta=TRUE))

tic()
ssjgl_res_emp2 <- map(dat_list_empirical, ~ ssjgl(Y=.x,penalty="fused",lambda0=1, lambda1=1,
                     lambda2=1, v1 = 1, v0s = seq(1e-04, 0.01, len = 5), a=1, b=1, doubly=TRUE, normalize=FALSE))
toc()


ssjgl_res_emp_test <- map(dat_list_empirical, ~ ssjgl(Y=.x,penalty="fused",lambda0=1, lambda1=1,
                     lambda2=1, v1 = 1, v0s = 0.04, a=1, b=1, doubly=TRUE, normalize=FALSE))

tic()
ssjgl_res_unif <- map(dat_list_uniform, ~ ssjgl(Y=.x,penalty="fused",lambda0=1, lambda1=1,
                     lambda2=1, v1 = 1, v0s = seq(1e-04, 0.01, len = 10), a=1, b=1, doubly=TRUE, normalize=FALSE))
toc()




jgl_res_err_unif <- map2(jgl_res_unif,gold_list_uniform, ~calc_metrics(.x$theta, .y, 0.01, "uniform", 0.03)) %>%
  bind_rows(.id = "data") %>%
  mutate(method = "jgl")

ssjgl_res_err_unif <- map2(ssjgl_res_unif, gold_list_uniform, ~calc_metrics(.x$thetalist[[10]], .y, .01, "uniform", 0.03))%>%
  bind_rows(.id = "data") %>%
  mutate(method = "sjgl")

jgl_res_err_emp2 <- map2(jgl_res_emp_100,gold_list_empirical, ~calc_metrics(.x$theta, .y, 0.01, "uniform", 0.03))%>%
  bind_rows(.id = "data") %>%
  mutate(method = "jgl")

ssjgl_res_err_emp2 <- map2(ssjgl_res_emp2, gold_list_empirical, ~calc_metrics(.x$thetalist[[5]], .y, .01, "uniform", 0.03))%>%
  bind_rows(.id = "data") %>%
  mutate(method = "sjgl")

res_master_50_1000 <- bind_rows(jgl_res_err_unif, ssjgl_res_err_unif, jgl_res_err_emp, ssjgl_res_err_emp2) %>%
  mutate(p = p,
         n = n)

res_100_1000 <- get_results(n, p, gold_list_uniform = gold_list_uniform,
                            gold_list_empirical = gold_list_empirical)
```





Run FGL. Tune lambdas, run FGL with tuned parameters, capture metrics. 

```{r}
thresh = 0.01
fgl_random_low_empirical <- tune_jgl(dat_random_low$emp_dat,
                                     threshold = thresh, 
                                     truth = gold_random_low, 
                                     true_omega1 = gold_random_low$omega$o1_emp, 
                                     true_omega2 = gold_random_low$omega$o2_emp,
                                     setting = "FGL Random Graph Low Density Empirical Weights")

fgl_random_low_unif <- tune_jgl(dat_random_low$unif_dat,
                                     threshold = thresh, 
                                     truth = gold_random_low, 
                                     true_omega1 = gold_random_low$omega$o1_unif, 
                                     true_omega2 = gold_random_low$omega$o2_unif,
                                setting = "FGL Random Graph Low Density Uniform Weights"
                                )

fgl_random_high_empirical <- tune_jgl(dat_random_high$emp_dat,
                                     threshold = thresh, 
                                     truth = gold_random_high, 
                                     true_omega1 = gold_random_high$omega$o1_emp, 
                                     true_omega2 = gold_random_high$omega$o2_emp,
                                     setting = "FGL Random Graph High Density Empirical Weights")

fgl_random_high_unif <- tune_jgl(dat_random_high$unif_dat,
                                     threshold = thresh, 
                                     truth = gold_random_high, 
                                     true_omega1 = gold_random_high$omega$o1_unif, 
                                     true_omega2 = gold_random_high$omega$o2_unif,
                                setting = "FGL Random Graph High Density Uniform Weights"
                                )


fgl_sf_low_empirical <- tune_jgl(dat_sf_low$emp_dat,
                                     threshold = thresh, 
                                     truth = gold_sf_low, 
                                     true_omega1 = gold_sf_low$omega$o1_emp, 
                                     true_omega2 = gold_sf_low$omega$o2_emp,
                                     setting = "FGL Scale Free Graph Low Density Empirical Weights")

fgl_sf_low_unif <- tune_jgl(dat_sf_low$unif_dat,
                                     threshold = thresh, 
                                     truth = gold_sf_low, 
                                     true_omega1 = gold_sf_low$omega$o1_unif, 
                                     true_omega2 = gold_sf_low$omega$o2_unif,
                                setting = "FGL Scale Free Graph Low Density Uniform Weights"
                                )

fgl_sf_high_empirical <- tune_jgl(dat_sf_high$emp_dat,
                                     threshold = thresh, 
                                     truth = gold_sf_high, 
                                     true_omega1 = gold_sf_high$omega$o1_emp, 
                                     true_omega2 = gold_sf_high$omega$o2_emp,
                                     setting = "FGL Scale Free Graph High Density Empirical Weights")

fgl_sf_high_unif <- tune_jgl(dat_sf_high$unif_dat,
                                     threshold = thresh, 
                                     truth = gold_sf_high, 
                                     true_omega1 = gold_sf_high$omega$o1_unif, 
                                     true_omega2 = gold_sf_high$omega$o2_unif,
                                setting = "FGL Scale Free Graph High Density Uniform Weights"
                                )



```

Now run Bayesian Spike and Slab fused graphical lasso on same 8 settings. 

```{r}
ssfgl_random_low_empirical <- run_ssjgl(dat_random_low$emp_dat,
                                     threshold = thresh, 
                                     truth = gold_random_low, 
                                     true_omega1 = gold_random_low$omega$o1_emp, 
                                     true_omega2 = gold_random_low$omega$o2_emp,
                                     setting = "SS-FGL Random Graph Low Density Empirical Weights")

ssfgl_random_low_unif <- run_ssjgl(dat_random_low$unif_dat,
                                     threshold = thresh, 
                                     truth = gold_random_low, 
                                     true_omega1 = gold_random_low$omega$o1_unif, 
                                     true_omega2 = gold_random_low$omega$o2_unif,
                                setting = "SS-FGL Random Graph Low Density Uniform Weights"
                                )

ssfgl_random_high_empirical <- run_ssjgl(dat_random_high$emp_dat,
                                     threshold = thresh, 
                                     truth = gold_random_high, 
                                     true_omega1 = gold_random_high$omega$o1_emp, 
                                     true_omega2 = gold_random_high$omega$o2_emp,
                                     setting = "SS-FGL Random Graph High Density Empirical Weights")

ssfgl_random_high_unif <- run_ssjgl(dat_random_high$unif_dat,
                                     threshold = thresh, 
                                     truth = gold_random_high, 
                                     true_omega1 = gold_random_high$omega$o1_unif, 
                                     true_omega2 = gold_random_high$omega$o2_unif,
                                setting = "SS-FGL Random Graph High Density Uniform Weights"
                                )


ssfgl_sf_low_empirical <- run_ssjgl(dat_sf_low$emp_dat,
                                     threshold = thresh, 
                                     truth = gold_sf_low, 
                                     true_omega1 = gold_sf_low$omega$o1_emp, 
                                     true_omega2 = gold_sf_low$omega$o2_emp,
                                     setting = "SS-FGL Scale Free Graph Low Density Empirical Weights")

ssfgl_sf_low_unif <- run_ssjgl(dat_sf_low$unif_dat,
                                     threshold = thresh, 
                                     truth = gold_sf_low, 
                                     true_omega1 = gold_sf_low$omega$o1_unif, 
                                     true_omega2 = gold_sf_low$omega$o2_unif,
                                setting = "SS-FGL Scale Free Graph Low Density Uniform Weights"
                                )

ssfgl_sf_high_empirical <- run_ssjgl(dat_sf_high$emp_dat,
                                     threshold = thresh, 
                                     truth = gold_sf_high, 
                                     true_omega1 = gold_sf_high$omega$o1_emp, 
                                     true_omega2 = gold_sf_high$omega$o2_emp,
                                     setting = "SS-FGL Scale Free Graph High Density Empirical Weights")

ssfgl_sf_high_unif <- run_ssjgl(dat_sf_high$unif_dat,
                                     threshold = thresh, 
                                     truth = gold_sf_high, 
                                     true_omega1 = gold_sf_high$omega$o1_unif, 
                                     true_omega2 = gold_sf_high$omega$o2_unif,
                                setting = "SS-FGL Scale Free Graph High Density Uniform Weights"
                                )



```


List of results

```{r}


res_p100_n1000_newempweights <- bind_rows(fgl_random_high_unif, ssfgl_random_high_unif, 
                 fgl_random_low_unif, ssfgl_random_low_unif,
                 fgl_sf_high_unif, ssfgl_sf_high_unif,
                  fgl_sf_low_unif, ssfgl_sf_low_unif,
                 fgl_random_high_empirical, ssfgl_random_high_empirical, 
                 fgl_random_low_empirical,  ssfgl_random_low_empirical,
                 fgl_sf_high_empirical,ssfgl_sf_high_empirical,
                 fgl_sf_low_empirical, ssfgl_sf_low_empirical
                ) %>%
  mutate(across(where(is.numeric), round, 3))

save(res_p100_n1000_newempweights, file = "res_p100_n1000_newempweights.Rdata")

gt::gt(res_p100_n1000_newempweights)
```





```{r include = FALSE, eval = FALSE}
# testing code

diff_restrue <- (abs(gold_list_empirical$random_low$omega$o1-gold_list_empirical$random_low$omega$o2) > 0.1)*1
test <- as.matrix((diff_restrue))
diag(test) <- 0
test <- ssjgl_res_emp2$random_low$thetalist[[8]][[1]]

test <- abs(ssjgl_res_emp2$random_low$thetalist[[8]][[1]]-ssjgl_res_emp2$random_low$thetalist[[8]][[2]])
diag(test) <- 0

diff_res_est <-  (abs(ssjgl_res_emp2$random_low$thetalist[[8]][[1]]-ssjgl_res_emp2$random_low$thetalist[[8]][[2]]) > 0.1)*1
diag(diff_res_est) <- 0

g_diff_graph_true <- as.matrix(as_adjacency_matrix(igraph::union(igraph::difference(gold_list_empirical$random_low$g$g1, gold_list_empirical$random_low$g$g2), 
                                igraph::difference(gold_list_empirical$random_low$g$g2, gold_list_empirical$random_low$g$g1))))

  
diff_perf <- suppressMessages(evaluatePerformance(gold_list_empirical$random_low$g_diff_graph, diff_restrue))

diff_perf2 <- suppressMessages(evaluatePerformance(diff_restrue, diff_res_est))
  
diff_res_true <- (abs(thetas[[1]] - thetas[[2]]) > diff_thresh)*1

# now do calc for difference between true sigmas
threshold = .01
 curr_res1 <-  (abs(gold_list_empirical$random_low$omega$o1) > threshold)*1
  
  diag(curr_res1) = 0
  
curr_perf1 <- suppressMessages(evaluatePerformance(gold_list_empirical$random_low$g$g1, curr_res1))
  
curr_res2 <-  (abs(gold_list_empirical$random_low$omega$o2) > threshold)*1
  
diag(curr_res2) = 0
  
curr_perf2 <- suppressMessages(evaluatePerformance(gold_list_empirical$random_low$g$g2, curr_res2))
  
diff_res <- as.matrix(abs(curr_res1-curr_res2))

evaluatePerformance(diff_res, diff_restrue)
```

