---
title: "Example simulation setup"
output: pdf_document
date: "2025-05-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(jewel)
library(tidyverse)
library(JGL)
library(pROC)
library(pheatmap)
library(MASS)

library(spikeyglass)

source("00_helper_functions.R")
source("01_generate_gold_standard_networks.R")

# read in reference weights
realDataHist = read.csv("mxDist.csv")
lower <- quantile(weights, .25)
upper <- quantile(weights, .75)

new_realdat <- realDataHist %>%
  filter(abs(mids) > upper) 

min_weight <- min(new_realdat$density[new_realdat$density > 0])

new_realdat <- new_realdat %>%
  mutate(density = ifelse(density ==0, min_weight, density))
```

Generate gold standard networks


First generate graph for network 1. We are generating under 2 different topologies: random or scale free. 

```{r}
set.seed(1219)

# low density
dens1 = 0.06


# high density
dens2 = 0.2
  
K <- 2 # number of groups
p <- 50# number of vertices
n <- 1000 # number of samples per group

# number of subnetworks
L <- 4
p_sub <- p/L  # features per subnetwork


# percent of edges to rewire
perc <- 0.1

g1_random_low = sample_gnp(p, dens1)
g1_random_high = sample_gnp(p, dens2)

g1_islands = sample_islands(4, 25, 5/10, 1)

g1_sf_low = sample_pa(n=p, power=1, m=2, directed=F)
g1_sf_high = sample_pa(n=p, power=1, m=5, directed=F)


```


Now rewire the G1 graph to get G2, then set edge weights in two ways: one using empirical distribution (Shutta) and another using uniform distribution (Plaksienko). 

```{r}
gold_random_low <- gen_gold(g1_random_low, perc, new_realdat)
gold_random_high <- gen_gold(g1_random_high, perc, new_realdat)
gold_sf_low <- gen_gold(g1_sf_low, perc, new_realdat)
gold_sf_high <- gen_gold(g1_sf_high, perc, new_realdat)
```

Now generate the data. 

```{r}
dat_random_low <- gen_dat(gold_random_low, n)
dat_random_high <- gen_dat(gold_random_high, n)
dat_sf_low <- gen_dat(gold_sf_low, n)
dat_sf_high <- gen_dat(gold_sf_high, n)
```

Run FGL. Tune lambdas, run FGL with tuned parameters, capture metrics. 

```{r}
thresh = 0.01
fgl_random_low_empirical <- tune_jgl(dat_random_low$emp_dat,
                                     threshold = thresh, 
                                     truth = gold_random_low, 
                                     true_omega1 = gold_random_low$omega$o1_emp, 
                                     true_omega2 = gold_random_low$omega$o2_emp,
                                     setting = "FGL Random Graph Low Density Empirical Weights")

fgl_random_low_unif <- tune_jgl(dat_random_low$unif_dat,
                                     threshold = thresh, 
                                     truth = gold_random_low, 
                                     true_omega1 = gold_random_low$omega$o1_unif, 
                                     true_omega2 = gold_random_low$omega$o2_unif,
                                setting = "FGL Random Graph Low Density Uniform Weights"
                                )

fgl_random_high_empirical <- tune_jgl(dat_random_high$emp_dat,
                                     threshold = thresh, 
                                     truth = gold_random_high, 
                                     true_omega1 = gold_random_high$omega$o1_emp, 
                                     true_omega2 = gold_random_high$omega$o2_emp,
                                     setting = "FGL Random Graph High Density Empirical Weights")

fgl_random_high_unif <- tune_jgl(dat_random_high$unif_dat,
                                     threshold = thresh, 
                                     truth = gold_random_high, 
                                     true_omega1 = gold_random_high$omega$o1_unif, 
                                     true_omega2 = gold_random_high$omega$o2_unif,
                                setting = "FGL Random Graph High Density Uniform Weights"
                                )


fgl_sf_low_empirical <- tune_jgl(dat_sf_low$emp_dat,
                                     threshold = thresh, 
                                     truth = gold_sf_low, 
                                     true_omega1 = gold_sf_low$omega$o1_emp, 
                                     true_omega2 = gold_sf_low$omega$o2_emp,
                                     setting = "FGL Scale Free Graph Low Density Empirical Weights")

fgl_sf_low_unif <- tune_jgl(dat_sf_low$unif_dat,
                                     threshold = thresh, 
                                     truth = gold_sf_low, 
                                     true_omega1 = gold_sf_low$omega$o1_unif, 
                                     true_omega2 = gold_sf_low$omega$o2_unif,
                                setting = "FGL Scale Free Graph Low Density Uniform Weights"
                                )

fgl_sf_high_empirical <- tune_jgl(dat_sf_high$emp_dat,
                                     threshold = thresh, 
                                     truth = gold_sf_high, 
                                     true_omega1 = gold_sf_high$omega$o1_emp, 
                                     true_omega2 = gold_sf_high$omega$o2_emp,
                                     setting = "FGL Scale Free Graph High Density Empirical Weights")

fgl_sf_high_unif <- tune_jgl(dat_sf_high$unif_dat,
                                     threshold = thresh, 
                                     truth = gold_sf_high, 
                                     true_omega1 = gold_sf_high$omega$o1_unif, 
                                     true_omega2 = gold_sf_high$omega$o2_unif,
                                setting = "FGL Scale Free Graph High Density Uniform Weights"
                                )



```

Now run Bayesian Spike and Slab fused graphical lasso on same 8 settings. 

```{r}
ssfgl_random_low_empirical <- run_ssjgl(dat_random_low$emp_dat,
                                     threshold = thresh, 
                                     truth = gold_random_low, 
                                     true_omega1 = gold_random_low$omega$o1_emp, 
                                     true_omega2 = gold_random_low$omega$o2_emp,
                                     setting = "SS-FGL Random Graph Low Density Empirical Weights")

ssfgl_random_low_unif <- run_ssjgl(dat_random_low$unif_dat,
                                     threshold = thresh, 
                                     truth = gold_random_low, 
                                     true_omega1 = gold_random_low$omega$o1_unif, 
                                     true_omega2 = gold_random_low$omega$o2_unif,
                                setting = "SS-FGL Random Graph Low Density Uniform Weights"
                                )

ssfgl_random_high_empirical <- run_ssjgl(dat_random_high$emp_dat,
                                     threshold = thresh, 
                                     truth = gold_random_high, 
                                     true_omega1 = gold_random_high$omega$o1_emp, 
                                     true_omega2 = gold_random_high$omega$o2_emp,
                                     setting = "SS-FGL Random Graph High Density Empirical Weights")

ssfgl_random_high_unif <- run_ssjgl(dat_random_high$unif_dat,
                                     threshold = thresh, 
                                     truth = gold_random_high, 
                                     true_omega1 = gold_random_high$omega$o1_unif, 
                                     true_omega2 = gold_random_high$omega$o2_unif,
                                setting = "SS-FGL Random Graph High Density Uniform Weights"
                                )


ssfgl_sf_low_empirical <- run_ssjgl(dat_sf_low$emp_dat,
                                     threshold = thresh, 
                                     truth = gold_sf_low, 
                                     true_omega1 = gold_sf_low$omega$o1_emp, 
                                     true_omega2 = gold_sf_low$omega$o2_emp,
                                     setting = "SS-FGL Scale Free Graph Low Density Empirical Weights")

ssfgl_sf_low_unif <- run_ssjgl(dat_sf_low$unif_dat,
                                     threshold = thresh, 
                                     truth = gold_sf_low, 
                                     true_omega1 = gold_sf_low$omega$o1_unif, 
                                     true_omega2 = gold_sf_low$omega$o2_unif,
                                setting = "SS-FGL Scale Free Graph Low Density Uniform Weights"
                                )

ssfgl_sf_high_empirical <- run_ssjgl(dat_sf_high$emp_dat,
                                     threshold = thresh, 
                                     truth = gold_sf_high, 
                                     true_omega1 = gold_sf_high$omega$o1_emp, 
                                     true_omega2 = gold_sf_high$omega$o2_emp,
                                     setting = "SS-FGL Scale Free Graph High Density Empirical Weights")

ssfgl_sf_high_unif <- run_ssjgl(dat_sf_high$unif_dat,
                                     threshold = thresh, 
                                     truth = gold_sf_high, 
                                     true_omega1 = gold_sf_high$omega$o1_unif, 
                                     true_omega2 = gold_sf_high$omega$o2_unif,
                                setting = "SS-FGL Scale Free Graph High Density Uniform Weights"
                                )



```


List of results

```{r}


res_p50_n1000 <- bind_rows(fgl_random_high_unif, ssfgl_random_high_unif, 
                 fgl_random_low_unif, ssfgl_random_low_unif,
                 fgl_sf_high_unif, ssfgl_sf_high_unif,
                  fgl_sf_low_unif, ssfgl_sf_low_unif,
                 fgl_random_high_empirical, ssfgl_random_high_empirical, 
                 fgl_random_low_empirical,  ssfgl_random_low_empirical,
                 fgl_sf_high_empirical,ssfgl_sf_high_empirical,
                 fgl_sf_low_empirical, ssfgl_sf_low_empirical
                )

save(res_p250_n10000, file = "fullres_n10000_p250.Rdata")

load()
gt::gt(res_p250_n10000)
```




